\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-11-03 parts-grn.tex

\modMM{The IG is not sufficient to unambiguously define the dynamics of the system. In particular, a component may be regulated by both a positive and negative interaction derived from two different components. To refine the dynamics, a parametrization had been added to the model \cite{snoussi1989qualitative}. This parametrization allows to define focal points, i.e. it clarifies the level towards which a component evolves depending on the expression of its regulators.
Some of the information included in the IG and the parametrization may appear as slighltly redundant. Especially, if the single parametrization were enriched with additional constraints (e.g., monotonicity requiring an ordering on the value of parameters), then it may directly capture the signs. However, distinguishing the IG and parametrization allows to decouple the graph (which is generally one of the prior knowledge from the biologists) from the constraints on its dynamics. It opened the way to numerous studies (e.g., necessary condition on sustained oscillations) solely based on the structure of the IG (e.g., the analysis of positive or negative circuits).}

@@

\begin{remark}[Parameters equivalence]
\label{rem:K-equiv}
\modLP{%
In the scope of the asychronous dynamics (\pref{def:dynamics}), one can remark
that some parameters values can be equivalent, i.e. the resulting dynamics is
the same.
It is notably the case with auto-regulations:
if $\GRNedge{a}{s}{t}{a}$,
then for any $\omega\subseteq \GRNreg{a}$,
two values $v$ and $v'$ of the parameter 
$K_{a,\omega\setminus \{a\}}$ are equivalent
if $v\geq t$ and $v'\geq t$.
Similary,
two values $v$ and $v'$ of the parameter
$K_{a,\omega\cup\{a\}}$ are equivalent 
if $v<t$ and $v'<t$.}
\end{remark}

>>>>

\modMM{The IG is not sufficient to unambiguously define the dynamics of the system. In particular, a component may be regulated by both a positive and negative interaction derived from two different components. To refine the dynamics, a parametrization had been added to the model \cite{snoussi1989qualitative}. This parametrization allows to define focal points, \ie it clarifies the level towards which a component evolves depending on the expression of its regulators.
Some of the information included in the IG and the parametrization may appear as slighltly redundant. Especially, if the single parametrization were enriched with additional constraints (e.g., monotonicity requiring an ordering on the value of parameters), then it may directly capture the signs. However, distinguishing the IG and parametrization allows to decouple the graph (which is generally one of the prior knowledge from the biologists) from the constraints on its dynamics. It opened the way to numerous studies (e.g., necessary condition on sustained oscillations) solely based on the structure of the IG (e.g., the analysis of positive or negative circuits).}

@@

\begin{remark}[Parameters equivalence]
\label{rem:K-equiv}
\modLP{%
In the scope of the asychronous dynamics (\pref{def:dynamics}), one can remark
that some parameters values can be equivalent, \ie the resulting dynamics is
the same.
It is notably the case with auto-regulations:
if $\GRNedge{a}{s}{t}{a}$,
then for any $\omega\subseteq \GRNreg{a}$,
two values $v$ and $v'$ of the parameter 
$K_{a,\omega\setminus \{a\}}$ are equivalent
if $v\geq t$ and $v'\geq t$.
Similary,
two values $v$ and $v'$ of the parameter
$K_{a,\omega\cup\{a\}}$ are equivalent 
if $v<t$ and $v'<t$.}
\end{remark}
